Analyses

### 2023-06-20 report/draft.Rmd
update analyses: lenient and strict stance perception

To answer whether there is an ideological or knowledge-basd annotation bias, we have conducted a two-by-two experiment. Tables \ref{tab:profilenl} and \ref{tab:profileus} demonstrate the average profile of respondents who annotate correctly and incorrectly (where respondents who annotated some stances correctly and some incorrectly are weighted by proportion (in)correct). In terms of demographics, there is not much of a difference. Yet, people who are incorrectly identifying stances are more left-wing oriented compared to those who are correct -- i.e. an average score of 4 for those who are incorrect vs. an average score of 5 for those who are correct. For other positions on issues or political knowledge, we do not see a difference in averages between those who are correctly and incorrectly identifying stances.

```{r "profilenl"}
load(here("data/intermediate/cleaned_data_nl.RData"))
load(here("data/intermediate/cleaned_data_us.RData"))
source(here("src/analysis/profile_resp.R"))
kbl(e1, booktabs =T, caption = "\\label{tab:conditions}Profile Dutch Stance Annotators") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "7cm") %>%
  column_spec(2, width = "7cm")
```
```{r "profileus"}
kbl(e1_us, booktabs =T, caption = "\\label{tab:conditions_us}Profile American Stance Annotators") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "7cm") %>%
  column_spec(2, width = "7cm")
```

@@

```{r results-h1, out.width= "95%", fig.align = 'center', fig.cap = "\\label{fig:results-h1} Ideological Distance"}
knitr::include_graphics(here("report/figures", "h1-3.png"))
```

@@

```{r results-h2, out.width = "95%", out.height = "75%", fig.align = 'center', fig.cap = "\\label{fig:results-h2} Results Level of Sentence Specification"}
knitr::include_graphics(here("report/figures", "h2-1.png"))
```

@@

```{r results-h3, out.width = "95%",  out.height = "75%", fig.align = 'center', fig.cap = "\\label{fig:results-h3} Results Masking Solution"}
knitr::include_graphics(here("report/figures", "h3-1.png"))
```

@@

```{r results-exploration1, out.height = "85%",out.width = "95%",, fig.align = 'center', fig.cap = "\\label{fig:results-exp1} Exploration: Issue Speficific Analyses"}
knitr::include_graphics(here("report/figures", "issues-1.png"))
```

@@

```{r results-exploration2, out.width = "95%", out.height= "75%", fig.align = 'center', fig.cap = "\\label{fig:results-exp2} Exploration: Interaction with Treatments"}
knitr::include_graphics(here("report/figures", "exploration-3.png"))
knitr::include_graphics(here("report/figures", "exploration-4.png"))
```

@@

```{r results-exploration3, out.width = "95%", fig.align = 'center', fig.cap = "\\label{fig:results-exp3} Exploration: Different Indicators of Ideological Distance (1)"}
knitr::include_graphics(here("report/figures", "exploration-1.png"))
```

```{r results-exploration4, out.width = "95%", fig.align = 'center', fig.cap = "\\label{fig:results-exp4} Exploration: Different Indicators of Ideological Distance (2)"}
knitr::include_graphics(here("report/figures", "exploration-2.png"))
```

```{r results-exploration5, out.width = "95%", fig.align = 'center', fig.cap = "\\label{fig:results-exp5} Exploration: Different Indicators of Ideological Distance (3)"}
knitr::include_graphics(here("report/figures", "exploration-3.png"))
```

```{r results-h2_expl, out.width = "95%", fig.align = 'center', fig.cap = "\\label{fig:results-h2-expl} Results Level of Sentence Specification"}
knitr::include_graphics(here("report/figures", "h2-3.png"))
```

>>>>

To answer whether there is an ideological or knowledge-basd annotation bias, we have conducted a two-by-two experiment. Tables \ref{tab:profilenl} and \ref{tab:profileus} demonstrate the average profile of respondents who annotate correctly and incorrectly (where respondents who annotated some stances correctly and some incorrectly are weighted by proportion (in)correct). In terms of demographics, there is not much of a difference. Yet, people who are incorrectly identifying stances are more left-wing oriented compared to those who are correct -- i.e. an average score of 4 for those who are incorrect vs. an average score of 5 for those who are correct. For other positions on issues or political knowledge, we do not see a difference in averages between those who are correctly and incorrectly identifying stances. This profile is quite similar for the lenient interpretation of what a stance is.

```{r "profilenl-strict"}
load(here("data/intermediate/cleaned_data_nl.RData"))
load(here("data/intermediate/cleaned_data_us.RData"))
source(here("src/analysis/profile_resp.R"))
kbl(e1_nlp, booktabs =T, caption = "\\label{tab:profilenl}Profile Dutch Stance Annotators") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "7cm") %>%
  column_spec(2, width = "7cm")
```

```{r "profileus"}
kbl(e1_us_nlp, booktabs =T, caption = "\\label{tab:conditions_us}Profile American Stance Annotators") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "7cm") %>%
  column_spec(2, width = "7cm")
```

@@

@@

\begin{landscape}
```{r results-h1, fig.align = 'center', fig.cap = "\\label{fig:results-h1} Ideological Distance", fig.pos="H", fig.show="hold",out.width = "49%", out.height="40%"}
knitr::include_graphics(c(here("report/figures", "h1-1.png"), here("report/figures", "h1-2.png")))
```
```{r results-h2, fig.align = 'center', fig.cap = "\\label{fig:results-h2} Results Level of Sentence Specification", fig.pos="H", fig.show="hold",out.width = "49%", out.height="40%"}
knitr::include_graphics(c(here("report/figures", "h2-1.png"), here("report/figures", "h2-2.png")))
```
\end{landscape}

@@

```{r results-h3, fig.align = 'center', fig.cap = "\\label{fig:results-h3} Results Masking Solution", fig.pos="H", fig.show="hold",out.width = "59%", out.height="50%"}
knitr::include_graphics(here("report/figures", "h3-1.png"))
```

@@

```{r results-exploration1, out.height = "85%",out.width = "95%",, fig.align = 'center', fig.cap = "\\label{fig:results-exp1} Exploration: Issue Speficific Analyses", eval = F}
knitr::include_graphics(c(here("report/figures", "issues-1.png")))
```

@@

```{r results-exploration2, out.width = "95%", out.height= "75%", fig.align = 'center', fig.cap = "\\label{fig:results-exp2} Exploration: Interaction with Treatments", eval = F}
knitr::include_graphics(here("report/figures", "exploration-3.png"))
knitr::include_graphics(here("report/figures", "exploration-4.png"))
```

@@

```{r results-exploration3, out.width = "95%", fig.align = 'center', fig.cap = "\\label{fig:results-exp3} Exploration: Different Indicators of Ideological Distance (1)", eval = F}
knitr::include_graphics(here("report/figures", "exploration-1.png"))
```

```{r results-exploration4, out.width = "95%", fig.align = 'center', fig.cap = "\\label{fig:results-exp4} Exploration: Different Indicators of Ideological Distance (2)", eval = F}
knitr::include_graphics(here("report/figures", "exploration-2.png"))
```

```{r results-exploration5, out.width = "95%", fig.align = 'center', fig.cap = "\\label{fig:results-exp5} Exploration: Different Indicators of Ideological Distance (3)", eval = F}
knitr::include_graphics(here("report/figures", "exploration-3.png"))
```

```{r results-h2_expl, out.width = "95%", fig.align = 'center', fig.cap = "\\label{fig:results-h2-expl} Results Level of Sentence Specification", eval = F}
knitr::include_graphics(here("report/figures", "h2-3.png"))
```

### 2023-06-20 src/analysis/Analysis.Rmd
update analyses: lenient and strict stance perception

## Baseline Model
```{r "baseline", fig.align="center", fig.height=4, fig.width=8}
source(here("src/analysis/baseline.R"))
b

b_b
```

```{r "issues", fig.align="center", fig.height=16, fig.width=8}
source(here("src/analysis/issue_specific.R"))
b_i

b_ib
```

## Ideological Bias hypothesis
```{r "h1", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/h1.R"))
p1

p1b

p1 / p1b +
  plot_layout(heights = c(1, 1.3)) + 
  plot_layout(guides = "collect") & theme(legend.position = 'bottom')

p1_2 / p1b2 +
  plot_layout(heights = c(1, 1.3)) 
```

## Overinterpretation Hypotheses
```{r "h2", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/h2.R"))
p2

p2b

p2c
```

## Masking Hypothesis
```{r "h3", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/h3.R"))
p3

p3b

p3c
```

## Exploration
```{r "exploration", fig.height=7, fig.width=8}
source(here("src/analysis/exploration.R"))
p_e1
p_e2
p_e3_1
p_e3_2
p_b
p_b2

source(here("src/analysis/profile_resp.R"))
kbl(e1, booktabs =T, caption = "\\label{tab:conditions}Profile Dutch Stance Annotators") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "7cm") %>%
  column_spec(2, width = "7cm")

kbl(e1_us, booktabs =T, caption = "\\label{tab:conditions_us}Profile American Stance Annotators") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "7cm") %>%
  column_spec(2, width = "7cm")
```

>>>>

## Baseline Model
```{r "baseline", fig.align="center", fig.height=4, fig.width=8}
source(here("src/analysis/baseline.R"))
b
rm(b_b, b1, b2, d, df, df_nl, df_us, tmp)
```

```{r "issues", fig.align="center", fig.height=16, fig.width=8}
source(here("src/analysis/issue_specific.R"))
b_i
rm(b1, b2, d, df, df_nl, df_us, tmp)
```

## Ideological Bias hypothesis
```{r "h1", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/h1.R"))
p1a
p1b
rm(df, df_nl, df_us, h1a, h1b, tmp)
```

## Overinterpretation Hypotheses
```{r "h2", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/h2.R"))
p2a
p2b
p2c1
p2c2
rm(df, df_nl, df_us, h2a, h2a_2, h2b, h2b_2, tmp, tmpp)
```

## Masking Hypothesis
```{r "h3", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/h3.R"))
p3a
p3b
p3c1
p3c2
rm(df, df_nl, df_us, h3a, h3a_2, h3b, h3b_2,h3b_bs, h3b_2bs, tmp, tmpp)
```

## Exploration
```{r "exploration", fig.height=7, fig.width=8}
source(here("src/analysis/exploration.R"))
p_b1
p_b2
p_e1a
p_e1b

source(here("src/analysis/profile_resp.R"))
kbl(e1_nlp, booktabs =T, caption = "\\label{tab:conditions}Profile Dutch Stance Annotators") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "7cm") %>%
  column_spec(2, width = "7cm")

kbl(e1_ss, booktabs =T, caption = "\\label{tab:conditions2}Profile Dutch Stance Annotators") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "7cm") %>%
  column_spec(2, width = "7cm")

kbl(e1_us_nlp, booktabs =T, caption = "\\label{tab:conditions_us}Profile American Stance Annotators") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "7cm") %>%
  column_spec(2, width = "7cm")

kbl(e1_us_ss, booktabs =T, caption = "\\label{tab:conditions_us2}Profile American Stance Annotators") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "7cm") %>%
  column_spec(2, width = "7cm")
```
